### 2022-02-11 preprint.tex
Remove useless subsection
Evaluation

\section{Motivating Examples}
\label{sec:motivating-example}

@@

\subsection{Safe Join}
\label{sec:safe-join}

@@

In the join benchmark, we see that the implicit-based implementation exceeds 30 seconds of compilation time around the 200 columns mark, and continues to grow quadratically.
This can be explained by the nature of implicit resolution, which might backtrack during its search.
The compilation time of the dependently-typed implementation grows linearly and stays below one second until the 350 columns mark.
We were able to observe similar trends in the concatenation benchmark.
These measurements were obtained by averaging 120 compilations on a warm compiler, and have been performed on an i7-7700K Processor running Oracle JVM 1.8.0 on Linux.

>>>>

\section{Motivating Example}
\label{sec:motivating-example}

@@

@@

In the join benchmark, we see that the implicit-based implementation exceeds 30 seconds of compilation time around the 200 columns mark, and continues to grow quadratically.
This can be explained by the nature of implicit resolution, which might backtrack during its search.
The compilation time of the dependently-typed implementation grows linearly and stays below one second until the 350 columns mark.
We were able to observe similar trends in the concatenation benchmark.
We obtained those measurements by averaging 120 independent compilations on a warm compiler, which we executed on an i7-7700K Processor running Oracle JVM 1.8.0 on Linux.

### 2022-02-11 symposium.tex
Evaluation

To assess the correctness of our library, we use the QT3TS test suite \citep{w3c1994xquery}, which contains about 1700 test cases for regular expressions \citep[perl-tests.xml]{w3c1994qt3ts}.
We select the subset of those tests which exercise successful matching with capturing groups, which amounts to a total of 183 tests.
Each test consists of one capturing group extraction, which we check againts the reference extraction.

\regexBars{A comparison of the compilation time (left) and execution time (right) of Scala's standard regex library (Std) against our library with its code duplicated runtime (Dup) and with its implicit-based runtime (Impl) on our test suite (lower is better).}

In this section... \Cref{fig:regexBars}.

>>>>

To assess the correctness of our library, we run our implementation against the QT3TS test suite \citep{w3c1994xquery}, which consists of about 1700 test cases for regular expressions \citep[perl-tests.xml]{w3c1994qt3ts}.
We select the subset of those tests that are positive (they match successfully) and exercises capturing groups, totaling 183 test cases, which we then collated to form a single benchmark.
We use this benchmark to evaluate the performance of our library in terms of compilation times and execution times.

\regexBars{A comparison of the compilation time (left) and execution time (right) of Scala's standard regex library (Std) against our library with its code duplicated runtime (Dup) and with its implicit-based runtime (Impl). Lower is better.}

In \Cref{fig:regexBars}, we show the results of our experiments, which compare Scala's standard regular expression library (Std) against two flavors of our library, one using our code duplicated runtime (Dup), presented in \Cref{subsec:we-ain-t-need-no-dependent-types}, and the other using our implicit-based runtime (Impl), presented in \Cref{subsec:implicit-based-extractor-synthesis}.

We obtained these results by averaging the measurements obtained over 2 hour runs, for each data point, which we executed on an i7-7700K Processor running Oracle JVM 1.8.0\_212 and Linux.
With these settings, we obtains margins of errors below \textpm1\%, with 99.9\% confidence (omitted from \Cref{fig:regexBars}).
